---
title: "Hutton Criteria Report"
output: word_document
params:
  primary: NA
  hutton: NA
  last_week: NA
always_allow_html: true
fontsize: 9pt
---
 
# Weather and monitoring of Hutton Criteria (2022)

##### Hutton Criteria
A Hutton Criteria occurs when two consecutive days have a minimum temperature of 10°C, and at least six hours of relative humidity at or above 90%.

\newpage

### Plot of weather observation for selected weather stations
```{r, echo=FALSE, warning=FALSE, message=FALSE}
params$primary +
  ggplot2::theme(
      legend.title = element_blank(),
      legend.text = element_text(size = 8),
      legend.position = "bottom"
    )
```

### Visualisation of Hutton Criteria for selected weather stations
```{r, echo=FALSE, warning=FALSE, message=FALSE}
params$hutton +
  ggplot2::scale_x_continuous(limits = c(1, 31), breaks = seq(1, 31, by = 10)) +
  ggplot2::theme(
    title = element_text(size = 10),
    panel.grid = element_blank(),
    legend.position = "bottom",
    axis.text = element_text(size = 8),
    axis.text.y.right = element_text(angle = 90, hjust = 0.5),
    legend.text = element_text(size = 6),
    legend.title = element_text(size = 8)
  )
```

\newpage

### Summary of observations from selected weather stations
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# TODO: make the table text smaller
knitr::kable(params$last_week)
```
